\documentclass[10pt]{article}

\usepackage{graphicx}
\usepackage[nohead,nofoot,left=1in,right=1in,top=0.75in,bottom=0.75in]{geometry}

\begin{document}

\newenvironment{mitemize}{
\begin{itemize}
  \setlength{\topsep}{0pt}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{itemize}
}
\setlength{\parskip}{0pt}
\setlength{\topskip}{0pt}
\pagestyle{empty}

\noindent {\bf \Huge Zachary Byrne \hspace{0.1cm}}{\Large BSc, EIT} \vspace{0.2cm}\\
Phone: \#REDACTED\# \hspace{1.5cm} Email: zacharyabyrne@gmail.com
\hspace{1.5cm} Github: github.com/zbyrne

\section*{Education}
\begin{description}
  \item [BSc] Computer Engineering (Traditional), \emph{University of Alberta} (Sept 2004 - May 2010)\\
\end{description}

\section*{Work Experience}
\noindent {\bf EMC Corporation} \hspace{0.5in} Edmonton, AB \hspace{0.5in} Nov 2015 - Present\\
\emph{Software Engineer}
\begin{mitemize}
  \item Worked in a small team to design and develop a new distributed
    cloud service product in Go.
  \item Applied RAFT consensus algorithm to implement replicated data
    structures and distributed locking.
  \item Used Docker to implement an integration testing environment in Python.
  \item Acted as team Scrum Master on a rotating basis.
\end{mitemize}

\noindent {\bf EMC Corporation} \hspace{0.5in} Edmonton, AB \hspace{0.5in} Apr 2012 - Oct 2015\\
\emph{Associate Software Engineer}
\begin{mitemize}
  \item Developed and maintained an integration testing system for the
    VPlex virtual storage controller in Python.
  \item Developed several server-client and peer-to-peer applications
    using REST and RPC interfaces.
  \item Migrated many components of the testing system to run in
    Docker.
  \item Reported and analysed bugs found by the testing system in both
    the VPlex firmware in C/C++ and the VPlex CLI in Java.
  \item Automated the building, distribution, and testing of VPlex's
    non-disruptive-upgrade package.
  \item Interviewed, selected, and mentored interns from the
    University of Alberta Engineering and Computer Science departments
    each year.
  \item Participated in code reviews focusing on style and
    architecture as well as promoting clean commit history and
    informative commit messages.
\end{mitemize}

\noindent {\bf Diesel Tech Industries} \hspace{0.5in} Edmonton, AB \hspace{0.5in} Feb 2011 - Mar 2012\\
\emph{Configuration Software/Firmware Developer}
\begin{mitemize}
  \item Developed electronics and software for a positive air shutoff
    system for diesel equipment in the oil and gas industry.
  \item Developed firmware for embedded control unit on NXP ARM 7
    microcontroller in C and assembly, including drivers for electric
    motors with feedback, RS232, pixel addressable LCD displays, CAN
    Bus, I2C, and USB CDC
  \item Designed gain-control circuit and developed firmware for
    tachometer board using magnetic flux from engine
    alternator. Presented engine speed to main controller over I2C.
  \item Developed Windows .Net application in Visual C++ for
    configuring and troubleshooting embedded controller over serial
    connection via USB, RS232, or WiFi.
\end{mitemize}

\newpage

\section*{Skills}
\begin{description}
  \item [\emph{Programming Languages}] Proficient in C, Python,
    Go. Familiar with C++, Java, C\#.
  \item [\emph{Scripting Languages}] Bash, Sed, Awk, Make.
  \item [\emph{Version Control}] Git.
  \item [\emph{Systems}] Linux, Docker.
  \item [\emph{Markup Languages}] \LaTeX, Markdown, HTML.
  \item [\emph{Text Editors}] Emacs.
  \item [\emph{IDEs}] Eclipse, Visual Studio, IAR Embedded Workbench.
\end{description}

\section*{Hobbies}
\subsection*{Programming}
  \begin{mitemize}
    \item Member of a programming club with coworkers working on
      problems from Google Code Jam, ACM competitions, and Matasano
      Cryptopals cryptography breaking challenges.
    \item See github.com/zbyrne for projects including solutions to
      Cryptopals set 1 in C++ and a Z80 emulator in both Go and
      Python.
    \item Contributer to the Python Standard Library.
  \end{mitemize}
\subsection*{Gaming}
  \begin{mitemize}
    \item Builds gaming PCs for personal use.
    \item Enjoys PC and tabletop role playing games, dungeon crawlers,
     and puzzle games.
  \end{mitemize}
\subsection*{Music}
  \begin{mitemize}
    \item Plays bass guitar.
    \item Plays banjo.
  \end{mitemize}
\subsection*{Brewing}
  \begin{mitemize}
    \item Brews all-grain beer of various styles.
  \end{mitemize}

\vspace{0.25in}
{\bf \centering REFERENCES AVAILABLE UPON REQUEST \par}

\end{document}
